\documentclass{article}                    % article class
 
\begin{document}                           % Begin document text
 
\section{{\textbf{Research problem or question}}}                % Print a section heading
What are the effects of strike on the students of Makerere University and the community within the University.
\textit{Thesis statement-strike has bad effect on the student and community within the University} and 
\textbf{here's how to make something boldface}.

{\small According to my research to my research during strikes at makerere, heavy deployment of police is always stayed all over the university to curb the strike while teagas canisters are also thrown to disperse students but students donot stop throwing stones to police and police vans while strikes seem to be the answer to students problems, they also cause alot of effects on studentsl.} Now the size
is back to normal.  
Notice the effect of ``grouping'' (enclosing a section in braces). 
The change to a smaller font only applies inside the braces. 
\textit{During the strikes, some students are locked up in the faculty buildings while most of the lecture rooms are empty distorting normal class hours and these lead to limit coverage of syllabus which inturn results into poor performance of students}
  
{\small The teagas causes heath risk to students in the long run and also students with problems like allergy asithma get heart attack. The teagas also pollutes the enviroment within the university. in the process of strike sonme students get injured and others die in the process}
{\small The strike has become anogtable culture of students and norm of life in Makerere University. The norm at Makerere University is that al strike start from lumumba hall and this has made the students who reside in the hall to be the most notorious at cumpas who are extremely rowdy. This creates bad reputation about the universityl.}
\\new
{\small Besides the students, the strike also affect the bussiness community within the university whereby, shopes, carteens and restaurants are locked because of the fear of attempts by students to damage their property and this retards their business progress.}
{\small During the strike, roads are blocked and tyres are burnt in the roads by students which hinders movement of cars.}
\section{{\textbf{Conclussion}}}
{\small Conclusively, for years, strikes have become away of bringing the attention of the administration at Makerere University and away of airing issues at hand and heart, but it could have along term effect on the reputation of Uganda's oldest and prestigious Institutionl.} 


                      % Print a subsection heading
Here's how to print dashes---the em-dash is written by typing three 
consecutive dashes; an en-dash (used between two numerals or in phone
numbers such as 764--9595) is written by typing two consecutive dashes. 
.''
 
\end{document}                             % The required last line
